Seasonal Adaptation

### 2019-11-25 writing/manuscript.Rmd
some rough methods added

@@

>>>>

### Basic Model

The method for calculating fitness is based on the work of @Wittmann2017 who originally proposed “segregation lift” as a general mechanism which may maintain balanced polymorphisms in a population under certain conditions.

The model first determines an individual's seasonal score ($z$) according to the equation: write equations later :)

where $n_{homo}$ is the number loci homozygous for the allele particular to that certain season and $d$ is a dominance parameter (which ranges between 0 and 1) and $n_{het}$ is the number of heterozygous loci. A dominance parameter of greater than one ($d > 1$) would correspond to a traditional heterozygote advantage, and therefore is not of interest in this model.

The model we propose differs from the _segregation lift model_ in a few important ways. For one, the loci in our model are located on diploid linked chromosomes, so the homologous pairs can recombine during a simulated meiosis before mating. Expand on why this may be interesting or important… Linked genes not require a $d > 0.5$. Some genes that may be important for seasonal traits (_i.e._ heat shock proteins) are located close to each other on chromosomes and have a high amount of linkage disequilibrium…

Our model also does not allow for “selfing” where an individual can asexually reproduce with itself to create an offspring… Other stufff maybe too

@@

### Simulated seasonal selection

The general outline for the seasonal selection simulation:

1. A population of $N$ individuals is created with a single diploid chromosome containing $L$ loci, all of which contribute to the individual’s seasonal fitness. 
2. Seasonal score is calculated according to Eqn 1 and the fitness is determined
Pairs of parents – of size $N$ – are sampled stochasticly with a probability proportional to their seasonal fitness. 
3. Each parent in the pair undergoes recombination with a per locus recombination rate of $P_c$ 
4. A chromosome from each parent is selected at random to create the diploid offsprings 
5. The new generation replaces the old generation in the population.
6. The new individuals undergo mutation with a per locus mutation probability $P_m$ which was fixed at the relatively high rate of 1x10^-14 [@Haag-Liautard2007]. 
7. A new generation begins and the current season is determined by the current generation and seasonal balance parameter $S_b$. 
8. A new generation of parents is selected according to their seasonal fitness and the process continues to cycle for a number of years.
9. Loci specific allele frequencies are tracked throughout the simulated evolutionary run.
